Unlocking Sensitivity for Visibility-based Estimators of the 21\,cm Reionization Power Spectrum

### 2017-07-22 Rotation paper/draft_working.tex
incorporated Aaron's last round comments
few corrections

\begin{figure}[h]
\includegraphics[width=\linewidth]{HeraAntpos}
\label{fig:HeraAntpos}
\caption{Planned Hydrogen Epoch of Reionization Array antenna configurations. HERA 37 is expected to complete and start collecting data in summer of 2017, and the other three are planned configurations in the next phases. For HERA350, only the 320 elements in the core are shown. }
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=\linewidth]{HeraAntpos}
\label{fig:HeraAntpos}
\caption{Planned Hydrogen Epoch of Reionization Array antenna configurations. HERA-37 is expected to complete and start collecting data in August of 2017, and the other three are planned configurations in the next phases. For HERA-350, only the 320 elements in the core are shown. }
\end{figure}
